---
title: "Unit 1 - 3 Review Starter"
author: "Group 2 (Gold team - Halite)"
date: "10-04-2021"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
sand_minerals <- read_csv("data/sand-minerals.csv")
location_descriptions <- read_csv("data/location-descriptions.csv")
density <- read_csv("data/density.csv")
solubility_hardness <- read_csv("data/solubility-hardness.csv")
```

## Exercises

### Exercise 1

```{r inspect-sand-minerals}
glimpse(sand_minerals)

names(sand_minerals)
```

In this data frame, there are 23 rows and 2 variables.

Each row is a mineral (either Quartz, Feldspar, or biotite) in any of ten different locations.

### Exercise 2

```{r inspect_other_dataframes}
glimpse(density)
glimpse(solubility_hardness)
glimpse(location_descriptions)

names(density)
names(solubility_hardness)
names(location_descriptions)

```
Density contains 3 rows and 2 variables
solubility hardness contains 3 rows and 3 variables
location descriptions contains 10 rows and 2 variables

the density row is the actual density of quartz, feldspar, and Biotite.
the solubility hardness row shows solubility as low, medium, or high.
the location description row descibes the 10 locations to be near water. from zulu

### Exercise 3

```{r join-mineral-properties}

sand_mineral_density <- left_join(sand_minerals, density)
sand_mineral_properties <- left_join(sand_mineral_density, solubility_hardness)

```

There `r nrow(sand_mineral_density)` rows in sand_mineral_density, compared to `r nrow(sand_minerals)` rows in sand_minerals. So they have the same number of rows, which checks out that sand_minerals was maintained in the join.

### Exercise 4

```{r sand-mineral-properties}
count(sand_mineral_properties, location)
```
```{r removal-of last-10-rows}
slice_head(sand_mineral_properties, n=10)
```
```{r decending-density}
sand_mineral_properties%>%
  arrange(desc(density))%>%
  slice_tail(n = 10)
  
```
```{r location-and-hardness}
sand_mineral_properties %>%
  select(location, hardness) %>%
  slice_tail(n=5)

```
```{r removal-of-NAs}
sand_mineral_properties %>%
  filter(hardness != "NA") %>%
  arrange(desc(density)) %>%
  slice_head(n=5)
```


### Exercise 5

Remove this text, and add your answer for Exercise 5 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.
